Variational Monte Carlo on bosonic systems

### 2018-03-11 project_1/article/article.tex

	\begin{table*}[ht]
		\centering
		\caption{Brute force Metropolis-Hasting at optimum value $\alpha = \frac{1}{2}$ in three dimensions. Step length = 0.1.}
		\begin{tabular}{c|ccc|ccc} 
			  & \multicolumn{3}{c|}{Analytic} & \multicolumn{3}{c}{Numeric} \\ \hline
			No. of particles & E($\alpha$) & $\sigma^2$(E) & CPU time [s] & E($\alpha$) & $\sigma^2$(E) & CPU time [s] \\ \hline
			1					 	&   1.5000		  & 0.0000			&  0.42562		& 1.29538		 & 0.10489		   & 0.69979  \\
			10						& 15.0000		  & 0.0000			&  0.78426 		& 7.70527		 & 3.91873		   & 7.06599	 \\
			100					&  150.0000	  & 0.0000			&  4.34369		& 74.22956 	 & 29.77369		   & 481.69100\\
			500					&	..				  & 0.0000			&  .. 					& ..	    			 & ..					   & \\ \hline
		\end{tabular}
	\end{table*}

>>>>

	\begin{table*}[ht]
		\centering
		\caption{Brute force Metropolis-Hasting at optimum value $\alpha = \frac{1}{2}$ in three dimensions. Step length = 0.1.}
		\begin{tabular}{c|ccc|ccc} 
			  & \multicolumn{3}{c|}{Analytic} & \multicolumn{3}{c}{Numeric} \\ \hline
			No. of particles & E($\alpha$) & $\sigma^2$(E) & CPU time [s] & E($\alpha$) & $\sigma^2$(E) & CPU time [s] \\ \hline
			1					 	&   1.5000		  & 0.0000			&  0.42562		& 1.29538		 & 0.10489		   & 0.69979  \\
			10						&  15.0000	  & 0.0000			&  0.78426 		& 7.70527		 & 3.91873		   & 7.06599	 \\
			100					&  150.0000	  & 0.0000			&  4.34369		& 74.22956 	 & 29.77369		   & 481.69100 \\
			500					&	750.0000	  & 0.0000			&  21.32269		& 362.01744	 & 51.52385         & 28409.41744\\ \hline
		\end{tabular}
	\end{table*}
